Report

### 2021-01-03 report.Rmd
Add NMDS analysis

```{r}
loadd(log_bm_net_group_f3y)
st_id_plot <- log_bm_net_group_f3y %>%
  filter(variable %in% get_com_str_var()) %>%
  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm))) +
  scale_color_viridis() +
  geom_text(aes(label = station)) +
  facet_wrap(~variable, scales = "free_y")
st_id_plot
st_network_to_plot <- c(513, 1453, 16654, 6020)
```

@@

species_trends2 %>%
  filter(linear_slope_pvalue < 0.05) %>%
  ggplot(aes(y = linear_slope, x = bm_slope, color = species)) +
  geom_point()

species_trend_cor <-
  species_trends2 %>%
  group_by(species) %>%
  summarise(
    spear = cor(linear_slope, bm_slope, method = c("spearman"), use = "pairwise.complete.obs"),
    n = n()
  )

species_trend_cor %>%
  filter(n >= 20) %>%
  ggplot(aes(y = spear, x = species)) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle = 45))
```

@@

```{r}
species_trend_cor %>%
  left_join(species_tlvl, by = "species") %>%
  filter(n > 20) %>%
  ggplot(aes(x = tlvl, y = spear)) +
  geom_point() +
  geom_smooth(method = "lm")
```

>>>>

## Temporal series of networks

```{r}
st_id_plot <- log_bm_net_group_f3y %>%
  filter(variable %in% get_com_str_var()) %>%
  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm))) +
  scale_color_viridis() +
  geom_text(aes(label = station)) +
  facet_wrap(~variable, scales = "free_y")
st_id_plot
st_network_to_plot <- c(513, 1453, 16654, 6020)
```

@@

species_trends2 %>%
  filter(linear_slope_pvalue < 0.05) %>%
  ggplot(aes(y = linear_slope, x = bm_slope, color = species)) +
  geom_point() +
  geom_smooth(method = "lm")

species_trend_cor <-
  species_trends2 %>%
  filter(linear_slope_pvalue < 0.05) %>%
  group_by(species) %>%
  summarise(
    spear = cor(linear_slope, bm_slope, method = c("spearman"), use = "pairwise.complete.obs"),
    n = n()
  )

species_trend_cor %>%
  filter(n >= 5) %>%
  ggplot(aes(y = spear, x = species)) +
  geom_bar(stat = "identity") +
  geom_label(aes(y = 0, label = paste("N=", n)), vjust = 1) +
  theme(axis.text.x = element_text(angle = 45))
```

@@

```{r}
species_trend_cor %>%
  left_join(species_tlvl, by = "species") %>%
  filter(n >= 5) %>%
  ggplot(aes(x = tlvl, y = spear)) +
  geom_label(aes(label = species)) +
  geom_smooth(method = "lm")
```

## Composition and biomass trajectory

```{r}
library(vegan)
myload(nmds, com_mat,envir = environment(), dir = get_mypath("data"))

bm_slope_df <- log_bm_net_group_f3y %>% 
  filter(variable == "connectance") %>%
  select(station, bm_slope, bm) %>%
  arrange(station)

loadd(com_analysis_data, op_data)
com_mat <- compute_com_mat(
  .op = ungroup(op_data) %>% filter(station %in% bm_slope_df$station),
  com = ungroup(com_analysis_data))

com <- com_mat %>% 
  arrange(station) 
#check:
all(com$station == bm_slope_df$station)
com <- com[, colSums(com != 0) > 0] %>%
  select(-station)

nmds <- metaMDS(com, k = 2, trymax = 100)

```{r}
diverging_pal <- c("#67001f", "#b2182b", "#d6604d", "#f4a582", "#fddbc7",
  "#f7f7f7", "#d1e5f0", "#92c5de", "#4393c3", "#2166ac", "#053061")

par(mfrow = c(1, 2))
stressplot(nmds)
title("Stress plot")
bluefunc <- colorRampPalette(c("lightyellow", "darkred"))
ordiplot(nmds,type="n")
orditorp(nmds,display="species",col="gray",air=0.01)
orditorp(nmds, display="sites",
  col= diverging_pal[findInterval(bm_slope_df$bm_slope, seq(-0.2,.2, length.out = length(diverging_pal)))],
   cex = findInterval(bm_slope_df$bm, seq(1, 4, 1))/2,
  air=0.01, pch = "+", labels = "+")
title("Color = ; Size of points = biomass")
